Recruiting Chapter

### 2021-05-04 educ250c_presentation.Rmd
presentation to 250c

@@

@@

@@

## Analysis sample

@@

@@

```{r plot-1mode-pubu, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
knitr::include_graphics('assets/figures/plot_1mode_pubu.png')
```

@@

**1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster**

```{r plot-1mode-all-pubu-outst, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.png')
```

>>>>

### Two-mode network objects

@@

<br>
*Two mode network of colleges (mode 1) visiting private high schools (mode 2), nodes colored by community cluster*
```{r, echo = FALSE}
# knitr::include_graphics('assets/figures/figure_5.pdf')
knitr::include_graphics('assets/figures/plot_2mode_all-1.png')
```

### One-mode network objects

@@

<br>
*One-mode network of private universities, edges between two universities weighted by the number of high schools they both visited, nodes colored by community cluster*
```{r, echo = FALSE}
# knitr::include_graphics('assets/figures/figure_5.pdf')
knitr::include_graphics('assets/figures/plot_1mode_privu-1.png')
```

### Ego networks

A limitation of our data collection and analysis is that it is based on a convenience sample of colleges and universities, as described above. Thus, for each college and university in our sample, we know all the private high schools they visited (assuming no measurement error). However, for each private high school in our sample, we only know visits they received from the set of 42 colleges/universities in our sample. Given this limitation, it may be useful to think of our data collection as resulting in 40 "ego networks."

Ego networks

- An "ego" is a single "focal" node (e.g., The University of Notre Dame). 
- An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p. XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->. 
- For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame. Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.

<br>
*Ego network of Emory University, nodes colored by geographic region*
```{r, echo = FALSE}
# knitr::include_graphics('assets/figures/figure_5.pdf')
knitr::include_graphics('assets/figures/emory_region-1.png')
```

@@

@@

<br>
<br>

@@

```{r plot-1mode-pubu, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
knitr::include_graphics('assets/figures/plot_1mode_pubu-1.png')
```

@@

**1-mode network for public institutions, out-of-state visits only, colored by cluster** 
```{r plot-1mode-pubu-outst, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
knitr::include_graphics('assets/figures/plot_1mode_pubu_outst-1.png')
```

**1-mode network for private and public universities, out-of-state visits only for public universities, colored by cluster**

```{r plot-1mode-all-pubu-outst, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
knitr::include_graphics('assets/figures/plot_1mode_u_pubu_outst-1.png')
```
